---
title: "Principal Component Analysis"
author: "Shantam Gupta"
date: "April 8, 2017"
output: html_document
---

```{r}
require(devtools)
require(ggbiplot)
```
#Reading the data
```{r}
final <- read.csv("final.csv")
train <- read.csv("train.csv")
test <- read.csv("test.csv")
```

Befor PCA Analysis we shall standardize our columns 

```{r}
pca_final <- final[,]
for(i in 5:8){
  mean <- mean(pca_final[,i])
  range <- max(pca_final[,i]) - min(pca_final[,i])
  for(j in 1 :288){
    pca_final[j,i] <- ((pca_final[j,i]- mean)/ range)
  }
}
```

#PCA Analysis
```{r}
pca <- prcomp(pca_final[,5:308],center = TRUE,scale. = TRUE) 
summary(pca)
```
#plotting the PCA

```{r}
plot(pca, type = "l")
```

```{r}
barplot( pca$sdev^2/sum(pca$sdev^2) , xlab="principle component", 
         ylab="% of variance")
barplot( cumsum( pca$sdev^2/sum(pca$sdev^2) ) , xlab="principle component", 
         ylab="cumulative % of variance" )
```

```{r}
# define a color for each sample 
myColor <- rep(NA, nrow(pca_final))
myColor[pca_final[,4]==1] <- "red" 
myColor[pca_final[,4]==0] <- "blue" 

# score plot
plot(pca$x[,1:2], col=myColor, pch=16, cex=2)
legend("topleft", pch=16, col=c("red", "blue"), c("Rating =1", "Rating =0"))
pca$x
     
```

The above plot helps to understand how many components to retain. The y- axis is the variance and x axis are the principal componets. 



#Biplots
```{r}
 ggbiplot(pca, obs.scale = 1, var.scale = 1, 
              groups = factor(pca_final$Rating), ellipse = TRUE, 
              circle = TRUE) +  scale_color_discrete(name = '') + theme(legend.direction = 'horizontal', 
              legend.position = 'top')


```



#Conclusion
Not enough separation in the first two dimensions(8.9 % for PC1 and 5.9 % for PC2). Because of low proportion of variance in each component of PCA it becomes difficult to use PCA for dimensionality reduction for further analysis in our project.